---
title: "Oxphos Analysis"
author: "Angèle COUTANT"
date: "2023-05-03"
output: html_document
---


                                    ###########################################
                                    ~     Importation des données scRNAseq    ~
                                    ###########################################

# Importation des données single-cell

```{r, echo=FALSE, include=FALSE}
library(Seurat)       # Importation des données/Quantification
library(scater)       # Control Qualité
library(sctransform)  # Normalisation par seurat
library(biomaRt)      # Re Annotation des gènes
library(AUCell) 
#library(MAST)         # Analyse différentielle
library(pROC)
library(ggplot2)
library(GSEABase)
library(cowplot)
library(RColorBrewer)
library(data.table)
#library(harmony)
# library(devtools)
# library(SCENT)
library(DescTools)
library(plyr)

source('/mnt/Commun/Single_cell/functions.R')
```

```{r, include = FALSE, message=FALSE}
all_GO = getGmt('/mnt/Commun/sc_Induction/Donnees/c5.go.bp.v2022.1.Hs.symbols.gmt')
pid <- 'Glycolyse'
rainbow_act = c('#339900', '#0066CC', "#E69F00", "#FFCC33", "#990033", "#CC0033")

if (pid == "OxPhos"){
   color = rainbow_act[3]
   color2 = rainbow_act[4]
   activity = "HALLMARK_OXIDATIVE_PHOSPHORYLATION"
   GO = all_GO[["GOBP_OXIDATIVE_PHOSPHORYLATION"]]@geneIds 
   gmtFile <- "/mnt/Commun/sc_Induction/Donnees/h.all.v6.2.symbols.gmt"
   geneSets <- getGmt(gmtFile)
   HM <- geneSets[[activity]]@geneIds
   mart <- useMart("ensembl", dataset="hsapiens_gene_ensembl")
   HM_list <- getBM(attributes=c('external_synonym', 'hgnc_symbol'), filters= "external_synonym" ,values= HM, mart=mart, uniqueRows=T, useCache = FALSE)
   HM_list2 <- getBM(attributes=c('external_synonym', 'hgnc_symbol'), filters= 'hgnc_symbol' ,values=HM, mart=mart, uniqueRows=T, useCache = FALSE)
   HM_list <- rbind(HM_list2, HM_list)
   HM <- unique(c(HM_list$external_synonym, HM_list$hgnc_symbol))
   # spe_HM = read.csv('/mnt/Commun/sc_Induction/Metabo/OxPhos_pred/HM_specific_OxPhos.csv')
   # spe_GO = read.csv('/mnt/Commun/sc_Induction/Metabo/OxPhos_pred/GO_specific_OxPhos.csv')
}

if (pid == 'Glycolyse'){
   color = rainbow_act[4]
   color2 = rainbow_act[3]
   all_GO = getGmt('/mnt/Commun/sc_Induction/Donnees/c5.go.bp.v2022.1.Hs.symbols.gmt')
   GO = all_GO[["GOBP_POSITIVE_REGULATION_OF_GLUCOSE_METABOLIC_PROCESS"]]@geneIds
   gmtFile <- "/mnt/Commun/sc_Induction/Donnees/h.all.v6.2.symbols.gmt"
   geneSets <- getGmt(gmtFile)
   activity = "HALLMARK_GLYCOLYSIS"
   HM <- geneSets[[activity]]@geneIds
   mart <- useMart("ensembl", dataset="hsapiens_gene_ensembl")
   HM_list <- getBM(attributes=c('external_synonym', 'hgnc_symbol'), filters= "external_synonym" ,values= HM, mart=mart, uniqueRows=T, useCache = FALSE)
   HM_list2 <- getBM(attributes=c('external_synonym', 'hgnc_symbol'), filters= 'hgnc_symbol' ,values=HM, mart=mart, uniqueRows=T, useCache = FALSE)
   HM_list <- rbind(HM_list2, HM_list)
   HM <- unique(c(HM_list$external_synonym, HM_list$hgnc_symbol))
   # spe_HM = read.csv('/mnt/Commun/sc_Induction/Metabo/Glycolyse_pred/HM_specific_Glyco.csv')
   spe_GO = read.csv('/mnt/Commun/sc_Induction/Metabo/Glycolyse_pred/GO_specific_Glyco.csv')

}

setwd('/mnt/Commun/sc_Induction/Metabo')

Arnaud = read.csv('/mnt/Commun/sc_Induction/Donnees/union_list_arnaud.csv')
Arnaud = as.vector(unlist(Arnaud))
```


                                    ###########################################
                                    ~           QC et normalisation           ~
                                    ###########################################
                                    

### QC & Normalisation

```{r, echo=FALSE, include=FALSE}
# Single Cell experiment
sce_act <- Read10X(data.dir = sprintf('/mnt/Commun/sc_Induction/Metabo/Donnees/%s_sample_feature_bc_matrix/', pid))
sce_inact <- Read10X(data.dir = '/mnt/Commun/sc_Induction/Metabo/Donnees/Control_sample_feature_bc_matrix')
   
colnames(sce_act[['Gene Expression']]) <- gsub(' ', '', paste(colnames(sce_act[['Gene Expression']]), '_activ'))
colnames(sce_inact[['Gene Expression']]) <- gsub(' ', '', paste(colnames(sce_inact[['Gene Expression']]), '_inactiv'))

# Convert in Seurat objet
act_obj <- CreateSeuratObject(sce_act[['Gene Expression']], project = pid)
inact_obj <- CreateSeuratObject(sce_inact[['Gene Expression']], project = 'Control')

act_obj[["percent.mt"]] <- PercentageFeatureSet(act_obj, pattern = "^MT-")
inact_obj[["percent.mt"]] <- PercentageFeatureSet(inact_obj, pattern = "^MT-")
act_obj[["percent.rb"]] <- PercentageFeatureSet(act_obj, pattern = "^RP[SL]")
inact_obj[["percent.rb"]] <- PercentageFeatureSet(inact_obj, pattern = "^RP[SL]")

pdf(sprintf('Filters_%s.pdf', pid))

VlnPlot(act_obj, features = c("nFeature_RNA","nCount_RNA","percent.mt","percent.rb"), ncol = 4, pt.size = 0.1) & 
   theme(plot.title = element_text(size=10))
VlnPlot(inact_obj, features = c("nFeature_RNA","nCount_RNA","percent.mt","percent.rb"),ncol = 4, pt.size = 0.1) & 
   theme(plot.title = element_text(size=10))

par(mfrow = c(3,1), mar = c(4, 4, 1, 3))

hist(act_obj$nCount_RNA, breaks = 50, xlab = '', main = '', col = color) 
abline(v=10000, col = 'red', lwd=2)
abline(v=80000, col='red', lwd=2)
plot(act_obj$percent.mt ~ act_obj$nCount_RNA, xlab = '', ylab = 'percent.mt', pch =16)
abline(h=5, col='red', lwd=2)
plot(act_obj$nFeature_RNA ~ act_obj$nCount_RNA, xlab = sprintf('nCount RNA',pid), ylab = 'n_features', pch =16)
abline(h=500, col='red', lwd=2)

hist(inact_obj$nCount_RNA, breaks = 50 , xlab = '', main ='', col = 'grey') 
abline(v=10000, col = 'red', lwd=2)
abline(v=80000, col='red', lwd=2)
plot(inact_obj$percent.mt ~ inact_obj$nCount_RNA, xlab = '', ylab = 'percent.mt', pch =16)
abline(h=5, col='red', lwd=2)
plot(inact_obj$nFeature_RNA ~ inact_obj$nCount_RNA, xlab = 'nCount RNA (Control)', ylab = 'n_features', pch =16)
abline(h=500, col='red', lwd=2)

rep(dev.off(), 2)

#Parameters

nfeature = 500
mt_percent = 5
max_count = 80000
min_count = 10000

act_tokeep = which(act_obj$nFeature_RNA > nfeature & act_obj$percent.mt < mt_percent & act_obj$nCount_RNA < max_count & act_obj$nCount_RNA > min_count)
inact_tokeep = which(inact_obj$nFeature_RNA > nfeature & inact_obj$percent.mt < mt_percent & inact_obj$nCount_RNA < max_count & inact_obj$nCount_RNA > min_count)

Activ <- CreateSeuratObject(counts = sce_act[['Gene Expression']][,act_tokeep], project = pid, min.cells = 3)
Inactiv <- CreateSeuratObject(counts = sce_inact[['Gene Expression']][,inact_tokeep], project = 'Control', min.cells = 3)

Activ = SCTransform(Activ)
Inactiv = SCTransform(Inactiv)

##### Normalisation #####

# By cell cycle

# s.genes <- cc.genes$s.genes
# g2m.genes <- cc.genes$g2m.genes
#mart <- useMart("ensembl", dataset="hsapiens_gene_ensembl")


s.gene = readRDS('/mnt/Commun/sc_Induction/Donnees/s.gene.Rds')
g2m.gene = readRDS('/mnt/Commun/sc_Induction/Donnees/g2m.gene.Rds')

cols_cycle <- c("S" = "orange", "G2M" = "darkolivegreen2", "G1" = "lightblue")


pdf(sprintf('/mnt/Commun/sc_Induction/Metabo/Cell_cycle_norm_%s.pdf', pid))
CC_act <- CellCycleScoring(object = Activ, s.features = s.gene, g2m.features = g2m.gene, set.ident = TRUE)
CC_inact <- CellCycleScoring(object = Inactiv, s.features = s.gene, g2m.features = g2m.gene, set.ident = TRUE)
CC_act.pca <- RunPCA(CC_act, features = c(s.gene, g2m.gene))
CC_inact.pca <- RunPCA(CC_inact, features = c(s.gene, g2m.gene))
DimPlot(CC_act.pca, cols = cols_cycle) + ggtitle(sprintf("Before Cell Cycle Norm (%s)", pid))
DimPlot(CC_inact.pca, cols = cols_cycle) + ggtitle("Before Cell Cycle Norm (Control)")

Activ <- SCTransform(CC_act, vars.to.regress = c("S.Score", "G2M.Score")) 
Inactiv <- SCTransform(CC_inact, vars.to.regress = c("S.Score", "G2M.Score"))
pca_act <- RunPCA(Activ, features = c(s.gene, g2m.gene))
pca_inact <- RunPCA(Inactiv, features = c(s.gene, g2m.gene))
DimPlot(pca_act, cols = cols_cycle) + ggtitle(sprintf("After Cell Cycle Norm (%s)", pid))
DimPlot(pca_inact, cols = cols_cycle) + ggtitle("After Cell Cycle Norm (Control)")

dev.off()
```

```{r}
# Choix de l'orientation de l'analyse : 
# - Controle VS Act1
# - Controle+Act1 VS Act2 (Mixt_Ctrl)

comb = 'Normal' #'Normal' #'Mixt_Ctrl'

if (comb != "Mixt_Ctrl"){
   setwd('/mnt/Commun/sc_Induction/Metabo/Donnees/')
   g = intersect(rownames(Activ), rownames(Inactiv))
   both = cbind(Inactiv@assays[["SCT"]]@counts[g,], Activ@assays[["SCT"]]@counts[g,])
   
   #Remove all zero after normalisation
   both = both[-which(apply(both, 1, sum)==0),]
   g = rownames(both)

   isActiv <- rep(0:1, c(ncol(Inactiv), ncol(Activ)))
   activStr <- as.factor(rep(c("inactive","active"), c(ncol(Inactiv), ncol(Activ))))
   
   # filtered data for scvelo
   Inact = as.matrix(Inactiv@assays[["SCT"]]@counts[g,])
   colnames(Inact) = gsub('_inactiv', '_Control', colnames(Inact))
   Act = as.matrix(Activ@assays[["SCT"]]@counts[g,])
   colnames(Act) = gsub('_activ', sprintf('_%s', pid), colnames(Act))
   # write.csv(Inact, 'Ctrl_filtered.csv')
   # write.csv(Act, sprintf('%s_filtered.csv',pid))
}

if (comb == 'Mixt_Ctrl'){
   if (pid == 'OxPhos'){
      Ctrl = read.csv('/mnt/Commun/sc_Induction/Metabo/Donnees/Ctrl_filtered.csv')
      Ctrl2 = read.csv('/mnt/Commun/sc_Induction/Metabo/Donnees/Glycolyse_filtered.csv')
      rownames(Ctrl) = Ctrl$X
      rownames(Ctrl2) = Ctrl2$X
      Ctrl = Ctrl[,-1]
      Ctrl2 = Ctrl2[,-1]
      common_genes = intersect(rownames(Ctrl), rownames(Ctrl2))
      Inactiv = cbind(Ctrl[common_genes,], Ctrl2[common_genes,])
      colnames(Inactiv) = gsub('.1_Glycolyse','-1_inactiv', colnames(Inactiv))
      colnames(Inactiv) = gsub('.1_Control','-1_inactiv', colnames(Inactiv))

   }
   
   if (pid == 'Glycolyse'){
      Ctrl = read.csv('/mnt/Commun/sc_Induction/Metabo/Donnees/Ctrl_filtered.csv')
      Ctrl2 = read.csv('/mnt/Commun/sc_Induction/Metabo/Donnees/OxPhos_filtered.csv')
      rownames(Ctrl) = Ctrl$X
      rownames(Ctrl2) = Ctrl2$X
      Ctrl = Ctrl[,-1]
      Ctrl2 = Ctrl2[,-1]
      common_genes = intersect(rownames(Ctrl), rownames(Ctrl2))
      Inactiv = cbind(Ctrl[common_genes,], Ctrl2[common_genes,])
      colnames(Inactiv) = gsub('.1_OxPhox','-1_inactiv', colnames(Inactiv))
      colnames(Inactiv) = gsub('.1_Control','-1_inactiv', colnames(Inactiv))
   }
   g = intersect(rownames(Activ), rownames(Inactiv))
   both = cbind(Inactiv[g,], as.matrix(Activ@assays[["SCT"]]@data)[g,])
}


isActiv <- rep(0:1, c(ncol(Inactiv), ncol(Activ)))
activStr <- as.factor(rep(c("inactive","active"), c(ncol(Inactiv), ncol(Activ))))

```


                        #######################################################
                        ~              Analysis from bootstraps                ~
                        #######################################################
                        
# Analysis from Bootstraps

### Import bootstraps

Bootstraps were made from JupyterNotebook (Script Python)

```{r}
Boots = list()
Boot = paste('boot', seq(1:40), sep='')

for (b in 1:40){
   Boots[[b]] = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/Bootstraps/boot%i_Glycolyse_OxPhos_Ctrl.csv', b))[,2]
}
```

```{r}
Best_Param = function(g, ntop, shared, id1, id2, col1, col2){
   All_param = list()

   for( b in 1:length(Boot)){
      boots = c()
      parametre = Wstat = pvalue = c()
      #pdf(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/%s/Distribution_PseudoT.pdf', g, cond))

      for (n in ntop){
         for (s in shared){
            print(c(n, s))
            PseudoT = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/%s/boot%i/Pseudotimes_%s_%s_%i_%i.csv', g, cond ,b, cond, g, n, s ))
            PseudoT_ctrl = PseudoT[grep(id1, PseudoT$X),]
            PseudoT_act = PseudoT[grep(id2, PseudoT$X),]
            par(mfrow = c(2,1))
            hist(PseudoT_ctrl$velocity_pseudotime, xlim =c(0,1), breaks = 100, col=col1, xlab = '', main= sprintf('Pseudotimes (%s) [%i_%i]', id1, n, s))
            abline(v=mean(PseudoT_ctrl$velocity_pseudotime), col = 'red',lwd=2)
            hist(PseudoT_act$velocity_pseudotime, xlim =c(0,1), breaks = 100, col=col2, main=sprintf('Pseudotimes (%s) [%i_%i]', id2, n, s), xlab='')
            abline(v=mean(PseudoT_act$velocity_pseudotime), col = 'red',lwd=2)

            Wstat = c(Wstat, as.vector(wilcox.test(PseudoT_ctrl$velocity_pseudotime, PseudoT_act$velocity_pseudotime)$statistic))
            #Wstat = c(Wstat, as.vector(wilcox.test(PseudoT_act$velocity_pseudotime, PseudoT_ctrl$velocity_pseudotime)$statistic))

            pvalue = c(pvalue, as.vector(wilcox.test(PseudoT_ctrl$velocity_pseudotime, PseudoT_act$velocity_pseudotime)$p.value))
            parametre = c(parametre, paste(n, s, sep='_'))
            boots = c(boots, Boot[b])
            # summary_act = summary(PseudoT_act$velocity_pseudotime)
            # summary_ctrl = summary(PseudoT_ctrl$velocity_pseudotime)
            # 
            # Dist = c(Dist, (summary_act[["3rd Qu."]] - summary_ctrl[["1st Qu."]]))
         }
      }

      pseudoT_Wilcox = data.frame(Bootstraps = boots, Parametres = parametre, W_stat = Wstat, p_value= pvalue)
      names(pseudoT_Wilcox)[3:4] =  paste(names(pseudoT_Wilcox)[3:4], sprintf('_%s',cond))
      All_param[[b]] = pseudoT_Wilcox
      #dev.off()
   }

   return(ldply(lapply(All_param, function(w) as.data.frame(w)), rbind))
   #return(pseudoT_Wilcox)
}
```

Here, you have to try all conditions to identifie best parameters from pseudotimes values
- Pseudotimes from Ctrl to Glyco
- Pseudotimes from Ctrl to OxPhos
- Pseudotimes from Oxphos to Glyco
- Pseudotimes from Glyco to Oxphos

As a reminder, pseudotimes were generated from scvelo + cellrank analysis (Script Python)

```{r, include = FALSE}
cond = 'OxPhos_Glycolyse'
id1 = 'OxPhos' #Control, OxPhos, Glycolyse
id2 = 'Glycolyse'
ntop = seq(50,300, 50)
shared = c(25,50,75,100)
g = 'HM_Glycolyse'

setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/%s', g, cond))

param = Best_Param(g, ntop, shared, id1, id2,color2, color)
write.csv(param, sprintf('All_param_%s_W2_25oct25.csv', cond))
#param = param[grep(max(param$Distance), param$Distance),'Parametres']
#param_O = param
```

### Select best parameters

```{r}
Ctrl_glyco_param = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Ctrl_Glycolyse/All_param_Ctrl_Glycolyse_W_25oct25.csv', g))
Ctrl_oxphos_param = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Ctrl_OxPhos/All_param_Ctrl_OxPhos_W_25oct25.csv', g))
Oxphos_glyco_param1 = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/OxPhos_Glycolyse/All_param_OxPhos_Glycolyse_W_25oct25.csv', g))
Oxphos_glyco_param2 = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/OxPhos_Glycolyse/All_param_OxPhos_Glycolyse_W2_25oct25.csv', g))

Comb_parameters = unique(Ctrl_glyco_param$Parametres)

W_l = list()

for (b in 1:length(Boot)){
   W = c()
   print(sprintf('Bootstrap %s', b))
   for (i in 1:length(Comb_parameters)){
      p = Comb_parameters[i]
      print(p)
      p1 = Ctrl_glyco_param[which(Ctrl_glyco_param$Parametres == p),][b,'W_stat._Ctrl_Glycolyse']
      p2 = Ctrl_oxphos_param[which(Ctrl_oxphos_param$Parametres == p),][b,'W_stat._Ctrl_OxPhos']
      p3.1 = Oxphos_glyco_param1[which(Oxphos_glyco_param1$Parametres == p),][b,'W_stat._OxPhos_Glycolyse']
      p3.2 = Oxphos_glyco_param2[which(Oxphos_glyco_param2$Parametres == p),][b,'W_stat._OxPhos_Glycolyse']
      p3 = max(p3.1, p3.2)
      W_tot = p1+p2+p3
      W = c(W,W_tot)
   }
   W_l[[b]] = W
}
names(W_l) = Boot
#names(Dist_l) = Boot


IDx_max_Wtot = lapply(W_l, function(x) which(x == max(x))[1])

#IDx_max_Dist = lapply(Dist_l, function(x) which(x == max(x))[1])

Best_param_per_boot = Comb_parameters[unlist(IDx_max_Wtot)]
#Best_param_per_boot = Comb_parameters[unlist(IDx_max_Dist)]
#Best_param = Comb_parameters[which(W == max(W))]

# PseudoT = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/without_boot/Oxphos_Glyco/Pseudotimes_Oxphos_Glyco_Arnaud_%s.csv', Best_param))
# PseudoT_ctrl = PseudoT[grep("OxPhos", PseudoT$X),]
# PseudoT_act = PseudoT[grep("Glycolyse", PseudoT$X),]
# Dist = abs(mean(PseudoT_ctrl$velocity_pseudotime) - mean(PseudoT_act$velocity_pseudotime)) > 0.25

# Dist =c()
# for (i in 1:length(Best_param_per_boot)){
#    PseudoT = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/without_boot/Oxphos_Glyco/Pseudotimes_Oxphos_Glyco_Arnaud_%s.csv',g,i,Best_param_per_boot[i]))
#    PseudoT_ctrl = PseudoT[grep("OxPhos", PseudoT$X),]
#    PseudoT_act = PseudoT[grep("Glycolyse", PseudoT$X),]
#    Dist = c(Dist, abs(mean(PseudoT_ctrl$velocity_pseudotime) - mean(PseudoT_act$velocity_pseudotime)) )
# }
# DF_best = data.frame(Best_param = Best_param_per_boot, Dist_Oxphos_Glyco = Dist)
#
#saveRDS(Best_param, 'Best_param_Glyco_Oxphos.Rds')
setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/', g))
write.csv(Best_param_per_boot, 'Best_param_per_boot_24oct25.csv')
#saveRDS(Best_param, 'Best_param_Glyco_Oxphos.Rds')

```

==> At this step, you can identifie the drivers genes from the best parameters.

### Validation in TCGA

Drivers have to be validated in the TCGA : 
 - Glycolyse drivers have to be overexpressed in kidney cancer
 - OxPhos drivers have to be overexpressed in liver cancer

```{r}
load('/mnt/Commun/sc_Induction/Metabo/Verif_TCGA_drivers/TCGA_data.RData')

Which_cancer = function( Drivers_G, Drivers_O, BC_data, Liver_data, Kidney_data, idb, condition, date){
   
   genes_to_remove = names(table(Kidney_data$Hybridization.REF)[which(table(Kidney_data$Hybridization.REF)>1)]) #Les doublons
   Drivers_G = intersect(Drivers_G, Kidney_data$Hybridization.REF)
   Drivers_O = intersect(Drivers_O, Kidney_data$Hybridization.REF)
   
   BreastCancer = BC_data[-which(BC_data$Hybridization.REF %in% genes_to_remove),]
   liver = Liver_data[-which(Liver_data$Hybridization.REF %in% genes_to_remove),]
   kidney = Kidney_data[-which(Kidney_data$Hybridization.REF %in% genes_to_remove),]
   
   rownames(BreastCancer) = BreastCancer$Hybridization.REF
   rownames(liver) = liver$Hybridization.REF
   rownames(kidney) = kidney$Hybridization.REF
   
   BreastCancer = BreastCancer[,-1]
   liver = liver[,-1]
   kidney = kidney[,-1]
   
   BC_focus = as.matrix(BreastCancer[which(rownames(BreastCancer) %in% c(Drivers_G, Drivers_O)),])
   Liver_focus = as.matrix(liver[which(rownames(liver) %in% c(Drivers_G, Drivers_O)),])
   Kidney_focus = as.matrix(kidney[which(rownames(kidney) %in% c(Drivers_G, Drivers_O)),])
   
   BC_focus = rbind(BC_focus[which(rownames(BC_focus) %in% Drivers_G),], BC_focus[which(rownames(BC_focus) %in% Drivers_O),])
   Liver_focus = rbind(Liver_focus[which(rownames(Liver_focus) %in% Drivers_G),], Liver_focus[which(rownames(Liver_focus) %in% Drivers_O),])
   Kidney_focus = rbind(Kidney_focus[which(rownames(Kidney_focus) %in% Drivers_G),], Kidney_focus[which(rownames(Kidney_focus) %in% Drivers_O),])
   
   colnames(BC_focus) = paste('BC_', colnames(BC_focus2), sep='')
   colnames(Liver_focus) = paste('Liver', colnames(Liver_focus2), sep='')
   colnames(Kidney_focus) = paste('Kidney', colnames(Kidney_focus2), sep='')
   rownames(BC_focus) = rownames(BC_focus)
   rownames(Liver_focus) = rownames(Liver_focus)
   rownames(Kidney_focus) = rownames(Kidney_focus)
   
   interest_mat = cbind(Liver_focus, Kidney_focus2)#, BC_focus))
   interest_mat_numeric = log2(matrix(as.numeric(interest_mat), ncol = ncol(interest_mat))+1)
   colnames(interest_mat_numeric) = colnames(interest_mat)
   rownames(interest_mat_numeric) = rownames(interest_mat)
   
   
   ### Keep significant genes in Kidney Cancer ==> Glycolyse
   
   #pdf(sprintf('Glyco_drivers_TCGA_boot_%s_24oct25.pdf', idb))
   d_glyco_spe = c()
   
   for (i in 1:length(Drivers_G)){
     # t_BC.L = t.test(as.numeric(Liver_focus[Drivers_G[i],]), as.numeric(BC_focus[Drivers_G[i],]))
      #t_BC.K = t.test(as.numeric(Kidney_focus[Drivers_G[i],]), as.numeric(BC_focus[Drivers_G[i],]))
      print(i)
      t_K.L = t.test(as.numeric(Kidney_focus[Drivers_G[i],]), as.numeric(Liver_focus[Drivers_G[i],]))
      
      vioplot(log2(as.numeric(Liver_focus[Drivers_G[i],])+1), log2(as.numeric(Kidney_focus[Drivers_G[i],])+1), # log2(as.numeric(BC_focus[Drivers_G[i],])+1),
              ylab = Drivers_G[i], xaxt='n', col = c('#339900','#FF9933'), main = sprintf("Glyco Drivers (%s)", set),  #,'#FF33CC'
              xlab = sprintf('t.test Kidney_Liver = %.4f', t_K.L$p.value)) #t.test Liver_BC = %.4f --- t.test Kidney_BC = %.4f --- t_BC.L$p.value, t_BC.K$p.value,
      axis(1, at=c(1,2), label= c('Liver', 'Kidney'))
      
      if (mean(log2(as.numeric(Kidney_focus[Drivers_G[i],])+1)) > mean(log2(as.numeric(Liver_focus[Drivers_G[i],])+1)) 
          #&& mean(log2(as.numeric(Kidney_focus[Drivers_G[i],])+1)) > mean(log2(as.numeric(BC_focus[Drivers_G[i],])+1))
          && t_K.L$p.value < 0.05 ){
          #&& t_BC.K$p.value < 0.05){
         d_glyco_spe = c(d_glyco_spe, Drivers_G[i] )
      }
   }
   #dev.off()
   write.csv(d_glyco_spe, sprintf('Drivers_Glycolyse_Specific_Kidney_%s_boot_%s_%s_%s.csv',set, idb, condition, date))
   
   ### Keep significant genes in Liver Cancer ==> OxPhos
   
   #pdf(sprintf('Oxphos_drivers_TCGA_boot_%s_24oct25.pdf', idb))
   d_oxphos_spe = c()

   for (i in 1:length(Drivers_O)){
      # t_BC.L = t.test(as.numeric(Liver_focus[Drivers_O[i],]), as.numeric(BC_focus[Drivers_O[i],]))
      # t_BC.K = t.test(as.numeric(Kidney_focus[Drivers_O[i],]), as.numeric(BC_focus[Drivers_O[i],]))
      t_K.L = t.test(as.numeric(Kidney_focus[Drivers_O[i],]), as.numeric(Liver_focus[Drivers_O[i],]))
      vioplot(log2(as.numeric(Liver_focus[Drivers_O[i],])+1), log2(as.numeric(Kidney_focus[Drivers_O[i],])+1), # log2(as.numeric(BC_focus[Drivers_O[i],])+1),
              ylab = Drivers_O[i], xaxt='n', col = c('#339900','#FF9933'), main = "Oxphos Drivers",
              xlab = sprintf('t.test Kidney_Liver = %.4f', t_K.L$p.value))
      axis(1, at=c(1,2), label= c('Liver', 'Kidney'))

      if (mean(log2(as.numeric(Liver_focus[Drivers_O[i],])+1)) > mean(log2(as.numeric(Kidney_focus[Drivers_O[i],])+1))
          #&& mean(log2(as.numeric(Liver_focus[Drivers_O[i],])+1)) > mean(log2(as.numeric(BC_focus[Drivers_O[i],])+1))
          && t_K.L$p.value < 0.05 
          #&& t_BC.L$p.value < 0.05
      ){
         d_oxphos_spe = c(d_oxphos_spe, Drivers_O[i] )
      }
   }
   #dev.off()
   write.csv(d_oxphos_spe, sprintf('Drivers_OxPhos_Specific_Liver_%s_boot_%s_%s_%s.csv',set, idb, condition, date))
}
```

```{r}
set = "HM_Glycolyse"
date = '27oct25'
# Parmis les plus significatifs, selection des 25,50,75... pour affiner la liste !
condition = 'TOP75' #TOP50' # All #TOP25
setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/3pop/%s', set, date))
# Les drivers de sortie, selection des itérations ayant les bons sites initiaux et terminaux pour la recherche de drivers
FileName = list.files(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/3pop/%s', set, date), pattern = sprintf('Term_OK_%s.csv',date)) 

for (f in 1:length(FileName)){
   print(f)
   if (grep("Initial_Glycolyse", FileName[f]) ==1){     # "Initial_OxPhos"
      if (set == 'GO_bioS_HM' | set == 'GO_Metabo_HM'){
         idBoot = str_split(FileName[f], '_')[[1]][6]
         idBoot = str_split(idBoot, 'boot')[[1]][2]
      }
      if (set == 'GO_bioS' | set == 'GO_Metabo' | set == 'GO_Glycolyse' | set == 'HM_Glycolyse'){
         idBoot = str_split(FileName[f], '_')[[1]][5]
         idBoot = str_split(idBoot, 'boot')[[1]][2]
      }
      print(idBoot)
      
      setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/3pop/%s', set, date))
      file = read.csv(FileName[f])
      
      drivers_o = file[which(file$OxPhos_corr > 0 & file$OxPhos_qval < 0.001),] # Filtre les drivers les plus significatifs
      drivers_g = file[which(file$Glycolyse_corr > 0 & file$Glycolyse_qval < 0.001),]
      
      if (condition == 'TOP25'){
         top = 25
         Best_drivers_OxPhos = drivers_o
         Oxphos_drivers = Best_drivers_OxPhos[order(Best_drivers_OxPhos$OxPhos_qval, decreasing = F),][1:top,'Gene']
         
         Best_drivers_Glyco = drivers_g
         Glyco_drivers = Best_drivers_Glyco[order(Best_drivers_Glyco$Glycolyse_qval, decreasing = F),][1:top,'Gene']   
      }
      if (condition == 'TOP50'){
         top = 50
         Best_drivers_OxPhos = drivers_o
         Oxphos_drivers = Best_drivers_OxPhos[order(Best_drivers_OxPhos$OxPhos_qval, decreasing = F),][1:top,'Gene']
         
         Best_drivers_Glyco = drivers_g
         Glyco_drivers = Best_drivers_Glyco[order(Best_drivers_Glyco$Glycolyse_qval, decreasing = F),][1:top,'Gene']
      }
      if (condition == 'TOP75'){
         top = 75
         Best_drivers_OxPhos = drivers_o
         Oxphos_drivers = Best_drivers_OxPhos[order(Best_drivers_OxPhos$OxPhos_qval, decreasing = F),][1:top,'Gene']
         
         Best_drivers_Glyco = drivers_g
         Glyco_drivers = Best_drivers_Glyco[order(Best_drivers_Glyco$Glycolyse_qval, decreasing = F),][1:top,'Gene']
      }
      
      if (condition == 'All'){
         Oxphos_drivers = drivers_o[which(drivers_o$OxPhos_corr > 0 & drivers_o$OxPhos_qval < 0.001),"Gene"]
         Glyco_drivers = drivers_g[which(drivers_g$Glycolyse_corr > 0 & drivers_g$Glycolyse_qval < 0.001),'Gene']
      }

      setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/3pop/%s/Verif_TCGA_Drivers', set, date))
      
      Which_cancer(Glyco_drivers, Oxphos_drivers, BC, Liver, Kidney, idBoot, condition, date) # Selection des gènes les plus significatif dans un cancer plutot qu'un autres
      }
}
```


                                    ############################################
                                    ~       AUCell : Enrichment analysis       ~
                                    ############################################

### AUCell prediction / Model evaluation

```{r}
npid = 'OxPhos' # L'autre activité
   
Boot = paste('Boot', seq(1:40), sep='')
s_AUCell = c(0.05, 0.1, 0.15, 0.2)

seuil_AUCell = list()
all_seuil_AUCell = list()

gset_ID_v = c('Drivers_Metabo_Glyco', 'Drivers_Metabo_HM_Glyco_TOP25', 'Drivers_Metabo_HM_Glyco_TOP_50', 'Drivers_Metabo_HM_Glyco_TOP_75')

# gset_ID_v = c('HM', 'GO', 'Drivers_Metabo_OxPhos', "Drivers_Metabo_HM_OxPhos", 'Drivers_Metabo_OxPhos_TOP25', 'Drivers_Metabo_OxPhos_TOP50', 'Drivers_Metabo_OxPhos_TOP75')

for (id in 1:length(gset_ID_v)){
   gset_ID = gset_ID_v[id]
   print(gset_ID)
   
   for (s in 1:length(s_AUCell)){
      aucell.v <- c()
      print(s_AUCell[s])
      
      for (b in 1:length(Boot)){
         print(sprintf("Bootstrap randomisation: n=%d", b))

         
         if(gset_ID == "HM"){
            print('HM')
            gset = HM
         }
         
         if(gset_ID == 'GO'){
            print('GO')
            gset = GO
         }
         
         if (gset_ID == 'Drivers_Metabo_OxPhos'){
            print("Setwd")
            setwd('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo/3pop/Verif_TCGA_Drivers/Without_boot/')
            fileName = list.files(pattern = 'Drivers_OxPhos')
            print(fileName)
            if (length(grep(sprintf('boot_%i_', b), fileName)) > 0){
               print('gset')
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if (length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               print("next")
               next
            }
         }
         
         if (gset_ID == 'Drivers_Metabo_HM_OxPhos'){
            print("Setwd")
            setwd('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo_HM/3pop/Verif_TCGA_Drivers/Without_TOP/')
            fileName = list.files(pattern = 'Drivers_OxPhos')
            print(fileName)
            if (length(grep(sprintf('boot_%i_', b), fileName)) > 0){
               print('gset')
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if (length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               print("next")
               next
            }
         }
         
         print("TOP25")
         if (gset_ID == 'Drivers_Metabo_OxPhos_TOP25'){
            setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo/3pop/Verif_TCGA_Drivers/TOP25/'))
            fileName = list.files(pattern = 'Drivers_OxPhos')
            if (length(grep(sprintf('boot_%i_', b), fileName)) > 0){
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if (length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               next
            }
         }
         
         print("TOP50")
         if (gset_ID == 'Drivers_Metabo_OxPhos_TOP50'){
            setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo/3pop/Verif_TCGA_Drivers/TOP50/'))
            fileName = list.files(pattern = 'Drivers_OxPhos')
            if (length(grep(sprintf('boot_%i_', b), fileName)) > 0){
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if(length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               next
            }
         }
         
         print("TOP75")
         if (gset_ID == 'Drivers_Metabo_OxPhos_TOP75'){
            setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo/3pop/Verif_TCGA_Drivers/TOP75/'))
            fileName = list.files(pattern = 'Drivers_OxPhos')
            if (length(grep(sprintf('boot_%i.csv', b), fileName)) > 0){
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if (length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               next
            }
         }

         if (gset_ID == 'Drivers_Metabo_HM_Glyco'){
            print("Setwd")
            setwd('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo_HM/3pop/24oct25/Verif_TCGA_Drivers/WhitoutTOP/')
            fileName = list.files(pattern = 'Drivers_Glycolyse')
            print(fileName)
            if (length(grep(sprintf('boot_%i_', b), fileName)) > 0){
               print('gset')
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if (length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               print("next")
               next
            }
         }
         
         print("TOP_25")
         if (gset_ID == 'Drivers_Metabo_HM_Glyco_TOP_25'){
            setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo_HM/3pop/24oct25/Verif_TCGA_Drivers/TOP25/'))
            fileName = list.files(pattern = 'Drivers_Glycolyse')
            if (length(grep(sprintf('boot_%i_', b), fileName)) > 0){
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if (length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               next
            }
         }
         
         print("TOP_50")
         if (gset_ID == 'Drivers_Metabo_HM_Glyco_TOP_50'){
            setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo_HM/3pop/24oct25/Verif_TCGA_Drivers/TOP50/'))
            fileName = list.files(pattern = 'Drivers_Glycolyse')
            if (length(grep(sprintf('boot_%i_', b), fileName)) > 0){
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if(length(grep(sprintf('boot_%i_', b), fileName)) == 0){
               next
            }
         }
         
         print("TOP_75")
         if (gset_ID == 'Drivers_Metabo_HM_Glyco_TOP_75'){
            # setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo_HM/3pop/Verif_TCGA_Drivers/TOP75/'))
            setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/GO_Metabo_HM/3pop/24oct25/Verif_TCGA_Drivers/TOP75'))
            #fileName = list.files(pattern = 'Drivers_Glycolyse')
            fileName = list.files(pattern = 'Drivers_Glycolyse')
            if (length(grep(sprintf('boot_%i.csv', b), fileName)) > 0){
               gset = read.csv(fileName[grep(sprintf('boot_%i_', b), fileName)])[,2]
            }
            if (length(grep(sprintf('boot_%i.', b), fileName)) == 0){
               next
            }
         }

         
         if (pid == 'Glycolyse'){
               subcells = Boots[[b]]
               subcells = gsub('OxPhos', 'Control', subcells)
            }
         
         if (pid == 'OxPhos'){
               subcells = Boots[[b]]
               subcells = gsub('Glycolyse', 'Control', subcells)
            }
         
         subcells = gsub('Control', 'inactiv', subcells)
         subcells = gsub(pid, 'activ', subcells)
         subcells = gsub(npid, 'inactiv', subcells)

         subcells = which(colnames(both) %in% subcells)

         discov <- both[,subcells]
         valid <- both[,-subcells]
         dactiv <- isActiv[subcells]
         vactiv <- isActiv[-subcells]

         # AUCell GSEA score
         geneSets[[activity]]@geneIds <- gset
         gs <- geneSets[[activity]]
  
         score = Score_AUCell(as.matrix(valid[,]), gs, s_AUCell[s])
         names(score) <- colnames(valid)
         
         vdat=data.frame(isActiv=vactiv, Score=score)
         aucell.roc=roc(isActiv ~ Score, data=vdat, levels=c("0", "1"))
         aucell.v <- c(aucell.v, auc(aucell.roc))
      }
      seuil_AUCell[[s]] = aucell.v
   }
names(seuil_AUCell) = s_AUCell
all_seuil_AUCell[[id]] = seuil_AUCell
}
names(all_seuil_AUCell) = gset_ID_v

setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/%s_pred/', pid))
```

```{r}
boxplot(all_seuil_AUCell$Drivers_Metabo_HM_Glyco_TOP_75, ylim = c(0.5,1), ylab = "Drivers_Metabo_HM_Glyco_TOP_75" , xlab="AUCell threshold")
medians <- sapply(all_seuil_AUCell$Drivers_Metabo_HM_Glyco_TOP_75, median)
for (i in 1:length(medians)) {
    text(x = i, y = medians[i] + 0.025, labels = round(medians[i], 3), cex = 0.8)
}

boxplot(all_seuil_AUCell$Drivers_Metabo_HM_Glyco_TOP_50, ylim = c(0.5,1), ylab = "Drivers_Metabo_HM_Glyco_TOP_50" , xlab="AUCell threshold")
medians <- sapply(all_seuil_AUCell$Drivers_Metabo_HM_Glyco_TOP_50, median)
for (i in 1:length(medians)) {
    text(x = i, y = medians[i] + 0.025, labels = round(medians[i], 3), cex = 0.8)
}

boxplot(all_seuil_AUCell$Drivers_Metabo_HM_Glyco_TOP25, ylim = c(0.5,1), ylab = "Drivers_Metabo_HM_Glyco_TOP_25" , xlab="AUCell threshold")
medians <- sapply(all_seuil_AUCell$Drivers_Metabo_HM_Glyco_TOP25, median)
for (i in 1:length(medians)) {
    text(x = i, y = medians[i] + 0.025, labels = round(medians[i], 3), cex = 0.8)
}

boxplot(all_seuil_AUCell$Drivers_Metabo_Glyco, ylim = c(0.5,1), ylab = "Drivers_Metabo_HM_glyco" , xlab="AUCell threshold")
medians <- sapply(all_seuil_AUCell$Drivers_Metabo_Glyco, median)
for (i in 1:length(medians)) {
    text(x = i, y = medians[i] + 0.025, labels = round(medians[i], 3), cex = 0.8)
}


dev.off()

saveRDS(all_seuil_AUCell, sprintf('all_seuil_AUCell_GO_Metabo_%s_combNorm.Rds', pid))

```



                                 ###############################################
                                 #               Without bootstrap             #
                                 ###############################################
                                 
# Analysis from all cells

## Select best parameters

```{r}
Best_Param = function(g, ntop, shared, id1, id2, col1, col2){
   All_param = list()
   parametre = Wstat = pvalue = c()
   pdf(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25/%s/Distribution_PseudoT_allCells.pdf', g, cond))
      
   for (n in ntop){
      for (s in shared){
         print(c(n, s))
         PseudoT = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25/%s/Pseudotimes_%s_%s_%s_27oct25.csv', g, cond , g, n, s ))
         PseudoT_ctrl = PseudoT[grep(id1, PseudoT$X),]
         PseudoT_act = PseudoT[grep(id2, PseudoT$X),]
         par(mfrow = c(2,1))
         hist(PseudoT_ctrl$velocity_pseudotime, xlim =c(0,1), breaks = 100, col=col1, xlab = '', main= sprintf('Pseudotimes (%s) [%s_%s]', id1, n, s))
         abline(v=mean(PseudoT_ctrl$velocity_pseudotime), col = 'red',lwd=2)
         hist(PseudoT_act$velocity_pseudotime, xlim =c(0,1), breaks = 100, col=col2, main=sprintf('Pseudotimes (%s) [%s_%s]', id2, n, s), xlab='')
         abline(v=mean(PseudoT_act$velocity_pseudotime), col = 'red',lwd=2)
         
         Wstat = c(Wstat, as.vector(wilcox.test(PseudoT_ctrl$velocity_pseudotime, PseudoT_act$velocity_pseudotime)$statistic))
         #Wstat = c(Wstat, as.vector(wilcox.test(PseudoT_act$velocity_pseudotime, PseudoT_ctrl$velocity_pseudotime)$statistic))
         
         pvalue = c(pvalue, as.vector(wilcox.test(PseudoT_ctrl$velocity_pseudotime, PseudoT_act$velocity_pseudotime)$p.value))
         parametre = c(parametre, paste(n, s, sep='_'))
      }
   }
   pseudoT_Wilcox = data.frame(Parametres = parametre, W_stat = Wstat, p_value= pvalue)
   names(pseudoT_Wilcox)[2:3] =  paste(names(pseudoT_Wilcox)[2:3], sprintf('_%s',cond))
   dev.off()
   return(pseudoT_Wilcox)
}
```

```{r}
g = 'HM_Glycolyse'
cond = 'OxPhos_Glyco'
id1 = "Glyco" #Control #Glyco #OxPhos
id2 = "OxPhos"
col1 = color2
col2 = color

ntop = seq(50, 300, 50)
shared = seq(25, 100, 25)

setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25/%s', g, cond))

param = Best_Param(g, ntop, shared, id1, id2, col1, col2)
write.csv(param, sprintf('All_param_%s_W2_27oct25.csv', cond))
```

```{r}
Ctrl_glyco_param = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25/Ctrl_Glyco/All_param_Ctrl_Glyco_W_27oct25.csv', g))
Ctrl_oxphos_param = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25/Ctrl_OxPhos/All_param_Ctrl_OxPhos_W_27oct25.csv', g))
Oxphos_glyco_param1 = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25/OxPhos_Glyco/All_param_OxPhos_Glyco_W_27oct25.csv', g))
Oxphos_glyco_param2 = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25/OxPhos_Glyco/All_param_OxPhos_Glyco_W2_27oct25.csv', g))

Comb_parameters = unique(Ctrl_glyco_param$Parametres)


W = c()
for (i in 1:length(Comb_parameters)){
   p = Comb_parameters[i]
   print(p)
   p1 = Ctrl_glyco_param[which(Ctrl_glyco_param$Parametres == p),][,'W_stat._Ctrl_Glyco']
   p2 = Ctrl_oxphos_param[which(Ctrl_oxphos_param$Parametres == p),][,'W_stat._Ctrl_OxPhos']
   p3.1 = Oxphos_glyco_param1[which(Oxphos_glyco_param1$Parametres == p),][,'W_stat._OxPhos_Glyco']
   p3.2 = Oxphos_glyco_param2[which(Oxphos_glyco_param2$Parametres == p),][,'W_stat._OxPhos_Glyco']
   p3 = max(p3.1, p3.2)
   W_tot = p1+p2+p3
   W = c(W,W_tot)
}

IDx_max_Wtot = which(W == max(W))

Best_param_all_cell = Comb_parameters[IDx_max_Wtot]

setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/%s/Without_boots/27oct25', g))
write.csv(Best_param_all_cell, 'Best_param_all_cells_27oct25.csv')

```






```{r, echo = FALSE, include = FALSE}
setwd(sprintf('/mnt/Commun/sc_Induction/Metabo/%s_pred', pid))

FCTHRESHOLD <- log2(1.5)
seuil_FDR <- 0.05

#s = 0.05  ############## A adapter !!!!! 

mostSigPerClust <- function(clustid, km, allp) {
   clustidx=which(km$cluster==clustid)
   return(sort(allp[clustidx])[1])
}


for (s in s_AUCell){
   print(' ############################################')
   print(sprintf('           Seuil AUCell = %s                  ', s))
   print(' ############################################')

   aucell.v <- c()
   r.aucL =  r.geneL = r.Roc =  list()
   hm.aucL =  hm.geneL = hm.Roc = list()
   hmgo.aucL =  hmgo.geneL = hmgo.Roc = list()
   go.aucL =  go.geneL = go.Roc = list()
   arnaud.aucL = arnaud.geneL = arnaud.Roc = list()
   drivers.aucL = drivers.geneL = drivers.Roc = list()
   speHM.aucL = speHM.geneL = speHM.Roc = list()
   speGO.aucL = speGO.geneL = speGO.Roc = list()
   speHMGO.aucL = speHMGO.geneL = speHMGO.Roc = list()

   
   for (b in 1:length(Boot)){
      print(sprintf("==========================> Bootstrap randomisation: n=%d <==========================", b))
      
      if (comb == 'Mixt_Ctrl'){
         if (pid == 'OxPhos'){
            subcells = Boots[[b]]
            subcells = gsub('Glycolyse', 'inactiv', subcells)
         }
         if (pid == 'Glycolyse'){
            subcells = Boots[[b]]
            subcells = gsub('OxPhos', 'inactiv', subcells)
         }
      }
         
      if (comb != 'Mixt_Ctrl'){
            subcells = Boots[[b]]
      }
         
      subcells = gsub('Control', 'inactiv', subcells)
      subcells = gsub(pid, 'activ', subcells)

      subcells = which(colnames(both) %in% subcells)

      
      valid <- both[,-subcells]
      discov <- both[,subcells]
      vactiv <- isActiv[-subcells]
      dactiv <- isActiv[subcells]
      
      file = read.csv(sprintf('/mnt/Commun/sc_Induction/Metabo/SCENT/Arnaud/3pop/all_drivers_Arnaud_boot%i.csv', b))
      subfile = file[c(1,grep(pid, colnames(file)))]
      drivers = subfile[which(subfile[,2] > 0 & subfile[,4] < 0.05),1]
      
      nclust = 6
      r.genes <- sample(rownames(both), 500)
      
      score = Score_AUCell(as.matrix(valid[,]), spe_GO, s)
      names(score) <- colnames(valid)
      vdat = data.frame(isActiv=vactiv, Score=score)
      aucell.roc=roc(isActiv ~ Score, data=vdat, levels=c("0", "1"))
      aucell.v <- c(aucell.v, auc(aucell.roc))
      
      sce <- SingleCellExperiment(colData=list(isActiv=as.factor(activStr[subcells])),
                                  assays=list(counts=both[,subcells]))
      
      filter <- rowSums(assay(sce)>5)>(length(subcells)*.15) ## Only genes with >5 reads in >15% of cells
      
      isRand <- rownames(both) %in% r.genes &
         rowSums(assay(sce)>1)>(length(subcells)*.15) ## Random genes with >1 reads in >1% of cells<

      isDrivers <- rownames(both) %in% drivers
      
      isspeHM <- rownames(both) %in% spe_HM[,1] &
         rowSums(assay(sce)>1)>(length(subcells)*.15)
      
      isspeGO<- rownames(both) %in% spe_GO[,1] &
         rowSums(assay(sce)>1)>(length(subcells)*.15)
      
      isspeHMGO <- rownames(both) %in% c(spe_HM[,1], spe_GO[,1]) &
         rowSums(assay(sce)>1)>(length(subcells)*.15)
      
      isHM <- rownames(both) %in% HM &
         rowSums(assay(sce)>1)>(length(subcells)*.15)
      
      isHMGO <- rownames(both) %in% c(HM, GO) &
         rowSums(assay(sce)>1)>(length(subcells)*.15)
      
      isGO <- rownames(both) %in% GO &
         rowSums(assay(sce)>1)>(length(subcells)*.15)
      
       isArnaud <-  rownames(both) %in% Arnaud &
          rowSums(assay(sce)>1)>(length(subcells)*.15)
      
      sce <- sce[filter | isDrivers | isHM | isHMGO | isGO | isArnaud | isRand,]
      print(table(filter | isDrivers | isHM | isHMGO | isGO | isArnaud | isRand))
      
      # sce <- sce[filter | isHM | isHMGO | isGO | isspeHM | isspeGO | isspeHMGO,] 
      # print(table(filter | isHM | isHMGO | isGO | isspeHM | isspeGO | isspeHMGO ))
      
      cdr2 <-colSums(assay(sce)>0)
      sce@colData$cngeneson = cdr2
      fdat=data.frame(primerid=rownames(both)[filter | isDrivers | isHM | isHMGO | isGO | isArnaud | isRand]) #
      #fdat=data.frame(primerid=rownames(both)[filter |  isHM | isHMGO | isGO | isspeHM | isspeGO | isspeHMGO]) #

      sca <- FromMatrix(sce@assays@data, colData(sce), fdat, check_sanity=F)
      cond <- factor(colData(sca)$isActiv)
      cond <- relevel(cond,"inactive") 
      colData(sca)$isActiv <- cond  
      zlmCond <- zlm(~isActiv + cngeneson, sca)
      
      summaryCond <- summary(zlmCond, doLRT='isActivactive')
      summaryDt <- summaryCond$datatable
      fcHurdle <- merge(summaryDt[contrast=='isActivactive' & component=='H',.(primerid, `Pr(>Chisq)`)], #hurdle P values
                        summaryDt[contrast=='isActivactive' & component=='logFC', .(primerid, coef, ci.hi, ci.lo)], by='primerid') #logFC coefficients
      fcHurdle[,fdr:=p.adjust(`Pr(>Chisq)`, 'fdr')]
      rownames(fcHurdle) = fcHurdle$primerid
      #fcHurdleSig <- merge(fcHurdle[fdr<.001 & abs(coef)>FCTHRESHOLD], as.data.table(mcols(sca)), by='primerid')
      fcHurdleSig <- merge(fcHurdle[fdr<seuil_FDR & abs(coef)>FCTHRESHOLD], as.data.table(mcols(sca)), by='primerid')
      setorder(fcHurdleSig, fdr)
      
      
      print('>>>>>>>>>>>>>>>> calcul distance')
      
      rset <- rownames(discov)[isRand]
      r.p = unlist(fcHurdle[rset,"fdr"])
      names(r.p)=rset
      r.dist = as.dist(1 - cor(t(as.matrix(discov[rset,])), method="spearman")/2)

      dset <- rownames(discov)[isDrivers]
      drivers.p = unlist(fcHurdle[dset,"fdr"])
      names(drivers.p)=dset
      drivers.dist = as.dist(1 - cor(t(as.matrix(discov[dset,])), method="spearman")/2)

      # dsetHM <- rownames(discov)[isspeHM]
      # spe.pHM = unlist(fcHurdle[dsetHM,"fdr"])
      # names(spe.pHM)=dsetHM
      # spe.distHM = as.dist(1 - cor(t(as.matrix(discov[dsetHM,])), method="spearman")/2)
      # 
      # dsetGO <- rownames(discov)[isspeGO]
      # spe.pGO = unlist(fcHurdle[dsetGO,"fdr"])
      # names(spe.pGO)=dsetGO
      # spe.distGO = as.dist(1 - cor(t(as.matrix(discov[dsetGO,])), method="spearman")/2)
      # 
      # dsetHMGO <- rownames(discov)[isspeHMGO]
      # spe.pHMGO = unlist(fcHurdle[dsetHMGO,"fdr"])
      # names(spe.pHMGO)=dsetHMGO
      # spe.distHMGO = as.dist(1 - cor(t(as.matrix(discov[dsetHMGO,])), method="spearman")/2)

      hmset <- rownames(discov)[isHM]
      hm.p = unlist(fcHurdle[hmset,"fdr"])
      names(hm.p)=hmset
      hm.dist = as.dist(1 - cor(t(as.matrix(discov[hmset,])), method="spearman")/2)
      
      hmgoset <- rownames(discov)[isHMGO]
      hmgo.p = unlist(fcHurdle[hmgoset,"fdr"])
      names(hmgo.p)=hmgoset
      hmgo.dist = as.dist(1 - cor(t(as.matrix(discov[hmgoset,])), method="spearman")/2)
      
      goset <- rownames(discov)[isGO]
      go.p = unlist(fcHurdle[goset,"fdr"])
      names(go.p)=goset
      go.dist = as.dist(1 - cor(t(as.matrix(discov[goset,])), method="spearman")/2)

      arnaudset <- rownames(discov)[isArnaud]
      arnaud.p = unlist(fcHurdle[arnaudset,"fdr"])
      names(arnaud.p)=arnaudset
      arnaud.dist = as.dist(1 - cor(t(as.matrix(discov[arnaudset,])), method="spearman")/2)


      
      for (n in 1:nclust) {
         print(sprintf("Fitting %d clusters(s)", n))
         
         print('>>>>>>>>>>>>>>>> calcul clusters r')
         r.clust = kmeans(r.dist, centers = n)
         r.genes = names(unlist(lapply(1:n, mostSigPerClust, km=r.clust, allp=r.p)))

         print('>>>>>>>>>>>>>>>> calcul clusters drivers')
         drivers.clust = kmeans(drivers.dist, centers = n)
         drivers.genes = names(unlist(lapply(1:n, mostSigPerClust, km=drivers.clust, allp=drivers.p)))
         
         # spe.clustHM = kmeans(spe.distHM, centers = n)
         # spe.genesHM = names(unlist(lapply(1:n, mostSigPerClust, km=spe.clustHM, allp=spe.pHM)))
         # 
         # spe.clustGO = kmeans(spe.distGO, centers = n)
         # spe.genesGO = names(unlist(lapply(1:n, mostSigPerClust, km=spe.clustGO, allp=spe.pGO)))
         # 
         # spe.clustHMGO = kmeans(spe.distHMGO, centers = n)
         # spe.genesHMGO = names(unlist(lapply(1:n, mostSigPerClust, km=spe.clustHMGO, allp=spe.pHMGO)))
         # 
         
         print('>>>>>>>>>>>>>>>> calcul clusters hm')
         hm.clust = kmeans(hm.dist, centers = n)
         hm.genes = names(unlist(lapply(1:n, mostSigPerClust, km=hm.clust, allp=hm.p)))
         
         print('>>>>>>>>>>>>>>>> calcul clusters hmgo')
         hmgo.clust = kmeans(hmgo.dist, centers = n)
         hmgo.genes = names(unlist(lapply(1:n, mostSigPerClust, km=hmgo.clust, allp=hmgo.p)))
         
         print('>>>>>>>>>>>>>>>> calcul clusters go')
         go.clust = kmeans(go.dist, centers = n)
         go.genes = names(unlist(lapply(1:n, mostSigPerClust, km=go.clust, allp=go.p)))

         print('>>>>>>>>>>>>>>>> calcul clusters Arnaud')
         arnaud.clust = kmeans(arnaud.dist, centers = n)
         arnaud.genes = names(unlist(lapply(1:n, mostSigPerClust, km=arnaud.clust, allp=arnaud.p)))

         
         print('AUCell r')
         if (length(r.genes) > 0){ ## Hack again
            score_r = Score_AUCell(as.matrix(valid[,]), r.genes, s)
            names(score_r) <- colnames(valid)
            vdat=data.frame(isActiv=vactiv, rg=score_r)
            aucell.roc=roc(isActiv ~ rg, data=vdat, levels=c("0", "1"))
         }
         if (length(r.aucL) < n) {
            r.aucL[[n]] <- c(auc(aucell.roc))
         } else {
            r.aucL[[n]] <- c(r.aucL[[n]], auc(aucell.roc))
         }

         if (length(r.geneL) < n) {
            r.geneL[[n]] <- c(r.genes)
         } else {
            r.geneL[[n]] <- c(r.geneL[[n]], r.genes)
         }
         if (length(r.Roc) < n) {
            r.Roc[[n]] <- c(aucell.roc)
         } else {
            r.Roc[[n]] <- c(r.Roc[[n]], aucell.roc)
         }

         print('AUCell drivers')
         if (length(drivers.genes) > 0){ ## Hack again
            score_d = Score_AUCell(as.matrix(valid[,]), drivers.genes, s)
            names(score_d) <- colnames(valid)
            vdat=data.frame(isActiv=vactiv, driver=score_d)
            aucell.roc=roc(isActiv ~ driver, data=vdat, levels=c("0", "1"))
         }
         if (length(drivers.aucL) < n) {
            drivers.aucL[[n]] <-  c(auc(aucell.roc))
         } else {
            drivers.aucL[[n]] <- c(drivers.aucL[[n]], auc(aucell.roc))
         }
         if (length(drivers.geneL) < n) {
            drivers.geneL[[n]] <- c(drivers.genes)
         } else {
            drivers.geneL[[n]] <- c(drivers.geneL[[n]], drivers.genes)
         }
         if (length(drivers.Roc) < n) {
            drivers.Roc[[n]] <- c(aucell.roc)
         } else {
            drivers.Roc[[n]] <- c(drivers.Roc[[n]], aucell.roc)
         }

         # if (length(spe.genesHM) > 0){ ## Hack again
         #    score_d = Score_AUCell(as.matrix(valid[,]), spe.genesHM, s)
         #    names(score_d) <- colnames(valid)
         #    vdat=data.frame(isActiv=vactiv, driver=score_d)
         #    aucell.roc=roc(isActiv ~ driver, data=vdat, levels=c("0", "1"))
         # }
         # if (length(speHM.aucL) < n) {
         #    speHM.aucL[[n]] <-  c(auc(aucell.roc))
         # } else {
         #    speHM.aucL[[n]] <- c(speHM.aucL[[n]], auc(aucell.roc))
         # }
         # if (length(speHM.geneL) < n) {
         #    speHM.geneL[[n]] <- c(spe.genesHM)
         # } else {
         #    speHM.geneL[[n]] <- c(speHM.geneL[[n]], spe.genesHM)
         # }
         # if (length(speHM.Roc) < n) {
         #    speHM.Roc[[n]] <- c(aucell.roc)
         # } else {
         #    speHM.Roc[[n]] <- c(speHM.Roc[[n]], aucell.roc)
         # }
         # 
         #       
         # 
         # if (length(spe.genesGO) > 0){ ## Hack again
         #    score_d = Score_AUCell(as.matrix(valid[,]), spe.genesGO, s)
         #    names(score_d) <- colnames(valid)
         #    vdat=data.frame(isActiv=vactiv, driver=score_d)
         #    aucell.roc=roc(isActiv ~ driver, data=vdat, levels=c("0", "1"))
         # }
         # if (length(speGO.aucL) < n) {
         #    speGO.aucL[[n]] <-  c(auc(aucell.roc))
         # } else {
         #    speGO.aucL[[n]] <- c(speGO.aucL[[n]], auc(aucell.roc))
         # }
         # if (length(speGO.geneL) < n) {
         #    speGO.geneL[[n]] <- c(spe.genesGO)
         # } else {
         #    speGO.geneL[[n]] <- c(speGO.geneL[[n]], spe.genesGO)
         # }
         # if (length(speGO.Roc) < n) {
         #    speGO.Roc[[n]] <- c(aucell.roc)
         # } else {
         #    speGO.Roc[[n]] <- c(speGO.Roc[[n]], aucell.roc)
         # }

         
         
         # if (length(spe.genesHMGO) > 0){ ## Hack again
         #    score_d = Score_AUCell(as.matrix(valid[,]), spe.genesHMGO, s)
         #    names(score_d) <- colnames(valid)
         #    vdat=data.frame(isActiv=vactiv, driver=score_d)
         #    aucell.roc=roc(isActiv ~ driver, data=vdat, levels=c("0", "1"))
         # }
         # if (length(speHMGO.aucL) < n) {
         #    speHMGO.aucL[[n]] <-  c(auc(aucell.roc))
         # } else {
         #    speHMGO.aucL[[n]] <- c(speHMGO.aucL[[n]], auc(aucell.roc))
         # }
         # if (length(speHMGO.geneL) < n) {
         #    speHMGO.geneL[[n]] <- c(spe.genesHMGO)
         # } else {
         #    speHMGO.geneL[[n]] <- c(speHMGO.geneL[[n]], spe.genesHMGO)
         # }
         # if (length(speHMGO.Roc) < n) {
         #    speHMGO.Roc[[n]] <- c(aucell.roc)
         # } else {
         #    speHMGO.Roc[[n]] <- c(speHMGO.Roc[[n]], aucell.roc)
         # }

         
         print('AUCell HM')
         if (length(hm.genes) > 0){ ## Hack again
            score_hm = Score_AUCell(as.matrix(valid[,]), hm.genes, s)
            names(score_hm) <- colnames(valid)
            vdat=data.frame(isActiv=vactiv, hmg=score_hm)
            aucell.roc=roc(isActiv ~ hmg, data=vdat, levels=c("0", "1"))
         }
         if (length(hm.aucL) < n) {
            hm.aucL[[n]] <- c(auc(aucell.roc))
         } else {
            hm.aucL[[n]] <- c(hm.aucL[[n]], auc(aucell.roc))
         }
         
         if (length(hm.geneL) < n) {
            hm.geneL[[n]] <- c(hm.genes)
         } else {
            hm.geneL[[n]] <- c(hm.geneL[[n]], hm.genes)
         }
         if (length(hm.Roc) < n) {
            hm.Roc[[n]] <- c(aucell.roc)
         } else {
            hm.Roc[[n]] <- c(hm.Roc[[n]], aucell.roc)
         }
         
         
         print('AUCell HMGO')
         if (length(hmgo.genes) > 0){ ## Hack again
            score_hmgo = Score_AUCell(as.matrix(valid[,]), hmgo.genes, s)
            names(score_hmgo) <- colnames(valid)
            vdat=data.frame(isActiv=vactiv, hmgo=score_hmgo)
            aucell.roc=roc(isActiv ~ hmgo, data=vdat, levels=c("0", "1"))
         }
         if (length(hmgo.aucL) < n) {
            hmgo.aucL[[n]] <- c(auc(aucell.roc))
         } else {
            hmgo.aucL[[n]] <- c(hmgo.aucL[[n]], auc(aucell.roc))
         }
         
         if (length(hmgo.geneL) < n) {
            hmgo.geneL[[n]] <- c(hmgo.genes)
         } else {
            hmgo.geneL[[n]] <- c(hmgo.geneL[[n]], hmgo.genes)
         }
         if (length(hmgo.Roc) < n) {
            hmgo.Roc[[n]] <- c(aucell.roc)
         } else {
            hmgo.Roc[[n]] <- c(hmgo.Roc[[n]], aucell.roc)
         }
         
         print('AUCell GO')
         if (length(go.genes) > 0){ ## Hack again
            score_go = Score_AUCell(as.matrix(valid[,]), go.genes, s)
            names(score_go) <- colnames(valid)
            vdat=data.frame(isActiv=vactiv, go=score_go)
            aucell.roc=roc(isActiv ~ go, data=vdat, levels=c("0", "1"))
         }
         if (length(go.aucL) < n) {
            go.aucL[[n]] <- c(auc(aucell.roc))
         } else {
            go.aucL[[n]] <- c(go.aucL[[n]], auc(aucell.roc))
         }

         if (length(go.geneL) < n) {
            go.geneL[[n]] <- c(go.genes)
         } else {
            go.geneL[[n]] <- c(go.geneL[[n]], go.genes)
         }
         if (length(go.Roc) < n) {
            go.Roc[[n]] <- c(aucell.roc)
         } else {
            go.Roc[[n]] <- c(go.Roc[[n]], aucell.roc)
         }
         
         
         print('AUCell Arnaud')
         if (length(arnaud.genes) > 0){ ## Hack again
            score_arnaud = Score_AUCell(as.matrix(valid[,]), arnaud.genes, s)
            names(score_arnaud) <- colnames(valid)
            vdat=data.frame(isActiv=vactiv, arnaud=score_arnaud)
            aucell.roc=roc(isActiv ~ arnaud, data=vdat, levels=c("0", "1"))
         }
         if (length(arnaud.aucL) < n) {
            arnaud.aucL[[n]] <- c(auc(aucell.roc))
         } else {
            arnaud.aucL[[n]] <- c(arnaud.aucL[[n]], auc(aucell.roc))
         }

         if (length(arnaud.geneL) < n) {
            arnaud.geneL[[n]] <- c(arnaud.genes)
         } else {
            arnaud.geneL[[n]] <- c(arnaud.geneL[[n]], arnaud.genes)
         }
         if (length(arnaud.Roc) < n) {
            arnaud.Roc[[n]] <- c(aucell.roc)
         }
      }
   }


   # saveRDS(r.aucL, sprintf('r_aucL_%s.RDS',s))
   # saveRDS(drivers.aucL, sprintf('drivers_aucL_%s.RDS', s))
   # saveRDS(speHM.aucL, sprintf('hm_aucL_%s_spe.RDS', s))
   # saveRDS(speGO.aucL, sprintf('go_aucL_%s_spe.RDS', s))
   # saveRDS(speHMGO.aucL, sprintf('hmgo_aucL_%s_spe.RDS', s))
   # 
   # 
   # saveRDS(arnaud.aucL, sprintf('arnaud_aucL_%s.RDS', s))
   # 
   # saveRDS(r.geneL, sprintf('r_geneL_%s.RDS', s))
   # saveRDS(drivers.geneL, sprintf('drivers_geneL_%s.RDS', s))
   # saveRDS(speHM.geneL, sprintf('hm_geneL_%s_spe.RDS', s))
   # saveRDS(speGO.geneL, sprintf('go_geneL_%s_spe.RDS', s))
   # saveRDS(speHMGO.geneL, sprintf('hmgo_geneL_%s_spe.RDS', s))
   # saveRDS(arnaud.geneL, sprintf('arnaud_geneL_%s.RDS', s))
   # 
   # saveRDS(aucell.v, sprintf('aucell_v_%s.RDS', s))
   
   
   r.m <- unlist(lapply(r.aucL, mean, na.rm=T))
   r.sd <- unlist(lapply(r.aucL, sd, na.rm=T))
   drivers.m <- unlist(lapply(drivers.aucL, mean, na.rm=T))
   drivers.sd <- unlist(lapply(drivers.aucL, sd, na.rm=T))
   # drivers.mHM <- unlist(lapply(drivers.aucLHM, mean, na.rm=T))
   # drivers.sdHM <- unlist(lapply(drivers.aucLHM, sd, na.rm=T))
   # 
   # drivers.mGO <- unlist(lapply(drivers.aucLGO, mean, na.rm=T))
   # drivers.sdGO <- unlist(lapply(drivers.aucLGO, sd, na.rm=T))
   # 
   # drivers.mHMGO <- unlist(lapply(drivers.aucLHMGO, mean, na.rm=T))
   # drivers.sdHMGO <- unlist(lapply(drivers.aucLHMGO, sd, na.rm=T))

   hm.m <- unlist(lapply(hm.aucL, mean, na.rm=T))
   hm.sd <- unlist(lapply(hm.aucL, sd, na.rm=T))
   hmgo.m <- unlist(lapply(hmgo.aucL, mean, na.rm=T))
   hmgo.sd <- unlist(lapply(hmgo.aucL, sd, na.rm=T))
   go.m <- unlist(lapply(go.aucL, mean, na.rm=T))
   go.sd <- unlist(lapply(go.aucL, sd, na.rm=T))
   
   # spehm.m <- unlist(lapply(speHM.aucL, mean, na.rm=T))
   # spehm.sd <- unlist(lapply(speHM.aucL, sd, na.rm=T))
   # spehmgo.m <- unlist(lapply(speHMGO.aucL, mean, na.rm=T))
   # spehmgo.sd <- unlist(lapply(speHMGO.aucL, sd, na.rm=T))
   # spego.m <- unlist(lapply(speGO.aucL, mean, na.rm=T))
   # spego.sd <- unlist(lapply(speGO.aucL, sd, na.rm=T))
   
   arnaud.m <- unlist(lapply(arnaud.aucL, mean, na.rm=T))
   arnaud.sd <- unlist(lapply(arnaud.aucL, sd, na.rm=T))
   
   pdf(sprintf('Prediction_meth2_%s_seuil_%s.pdf', pid, s))
   
   rainbow <- c('#CC0033', '#FF6633', '#FFCC33', '#99CC33', '#009933', '#009999', '#003399', '#330066', '#990066', '#660099', '#3300CC', '#0066CC' )
   
   plot(r.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[1], ylim=c(0.3,1), lwd=2, main = sprintf('Seuil AUCell = %.2f',s))
   points(r.m+r.sd, type="l", lty=2, col=rainbow[1], lwd=2)
   points(r.m-r.sd, type="l", lty=2, col=rainbow[1], lwd=2)
   
   points(hm.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[2], ylim=c(0.3,1), lwd=2)
   points(hm.m+hm.sd, type="l", lty=2, col=rainbow[2], lwd=2)
   points(hm.m-hm.sd, type="l", lty=2, col=rainbow[2], lwd=2)
   
   points(go.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[3], ylim=c(0.3,1), lwd=2)
   points(go.m+go.sd, type="l", lty=2, col=rainbow[3], lwd=2)
   points(go.m-go.sd, type="l", lty=2, col=rainbow[3], lwd=2)
   
   points(hmgo.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[4], ylim=c(0.3,1), lwd=2)
   points(hmgo.m+hmgo.sd, type="l", lty=2, col=rainbow[4], lwd=2)
   points(hmgo.m-hmgo.sd, type="l", lty=2, col=rainbow[4], lwd=2)
   
   
   # points(spehm.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[5], ylim=c(0.3,1), lwd=2, main = sprintf('Seuil AUCell = %.2f',s))
   # points(spehm.m+spehm.sd, type="l", lty=2, col=rainbow[5], lwd=2)
   # points(spehm.m-spehm.sd, type="l", lty=2, col=rainbow[5], lwd=2)
   # 
   # points(spego.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[6], ylim=c(0.3,1), lwd=2)
   # points(spego.m+spego.sd, type="l", lty=2, col=rainbow[6], lwd=2)
   # points(spego.m-spego.sd, type="l", lty=2, col=rainbow[6], lwd=2)
   # 
   # points(spehmgo.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[7], ylim=c(0.3,1), lwd=2)
   # points(spehmgo.m+spehmgo.sd, type="l", lty=2, col=rainbow[7], lwd=2)
   # points(spehmgo.m-spehmgo.sd, type="l", lty=2, col=rainbow[7], lwd=2)
   # 
   
   points(drivers.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[5], ylim=c(0.3,1), lwd=2)
   points(drivers.m+drivers.sd, type="l", lty=2, col=rainbow[5], lwd=2)
   points(drivers.m-drivers.sd, type="l", lty=2, col=rainbow[5], lwd=2)
   
   # points(drivers.mHM, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[5], ylim=c(0.3,1), lwd=2)
   # points(drivers.mHM+drivers.sdHM, type="l", lty=2, col=rainbow[5], lwd=2)
   # points(drivers.mHM-drivers.sdHM, type="l", lty=2, col=rainbow[5], lwd=2)
   # 
   # points(drivers.mGO, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[6], ylim=c(0.3,1), lwd=2)
   # points(drivers.mGO+drivers.sdGO, type="l", lty=2, col=rainbow[6], lwd=2)
   # points(drivers.mGO-drivers.sdGO, type="l", lty=2, col=rainbow[6], lwd=2)
   # 
   # points(drivers.mHMGO, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[7], ylim=c(0.3,1), lwd=2)
   # points(drivers.mHMGO+drivers.sdHMGO, type="l", lty=2, col=rainbow[7], lwd=2)
   # points(drivers.mHMGO-drivers.sdHMGO, type="l", lty=2, col=rainbow[7], lwd=2)
   # 
   points(arnaud.m, type="l", ylab="AUC score", xlab="Number of genes", col=rainbow[7], ylim=c(0.3,1), lwd=2)
   points(arnaud.m+arnaud.sd, type="l", lty=2, col=rainbow[7], lwd=2)
   points(arnaud.m-arnaud.sd, type="l", lty=2, col=rainbow[7], lwd=2)
   # 
   abline(h = mean(aucell.v), col="black", lwd=2)
   abline(h = mean(aucell.v)+sd(aucell.v), col="black", lwd=2, lty = 2)
   abline(h = mean(aucell.v)-sd(aucell.v), col="black", lwd=2, lty = 2)
   
   legend("topright",
          legend=c('random genes', "HM", "GO","HMGO", "Drivers (from Arnaud genes)", "Arnaud genes", 'spe_GO mean'),
          col=c(rainbow[1], rainbow[2], rainbow[3], rainbow[4], rainbow[5], rainbow[7], "black"), lty=1, lwd=2, bg="white", cex = 0.8)
   
      # legend("topright",
      #     legend=c("HM", "GO", "HMGO", 'HM spe', 'GO spe', 'HMGO spe', 'mean AUCell'),
      #     col=c(rainbow[2], rainbow[3], rainbow[4], rainbow[5], rainbow[6], rainbow[7], "black"), lty=1, lwd=2, bg="white", cex = 0.8)

   dev.off()
   
} #Fin boucle seuil AUCell

```
